\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Fast Castle}
\author{by @clrnd}
\date{July 2017}

\usepackage{graphicx}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=black,
}

\begin{document}

\maketitle

This is a guide to get into the Castle Age in Age of Empires 2 very fast.
Going Fast Castle is not a requirement to win, nor the only way to play the game.
Nevertheless it's an important technique because mastering it almost ensures domination over a player who doesn't.
Also it will give you an easy script to follow that, with practice, will give you the right intuition and knowledge so you can develop your own build order later on.

The Castle Age is important for two main reasons:

\begin{itemize}
  \item Building Town Centers increases your villager production which is critical
  \item It gives you a lot of offensive capabilities: Knights, Crossbows, Unique Units, etc.
\end{itemize}

\section*{Basics}

The following text is based on Resonance22's guide\footnote{\url{https://www.youtube.com/watch?v=zQ5NOGLd3PE}}.
First of all and most important:

\begin{itemize}
  \item Your TC should never be idle. It should always be producing villagers, researching a technology or going to the next Age.
  \item Your scout should always be scouting. It is crucial that you find your initial sheep and two boars.
\end{itemize}

Start by building two houses with your initial villagers and finding the sheep with your scout. If the sheep are hard to find, use your villagers too. With the sheep found and the houses built, start eating the sheep with all the villagers.

Boars need to be lured below your TC. To do this, make a villager shoot it twice, and the instantly run back to the TC, trying to make the boar walk trough it so it can be killed by your other villagers just below it.

Try to build a house every time you are 3 units from being housed. If you do get housed, research loom. You can also research loom also before clicking Feudal or before doing the boar lure to prevent losing a villager.

In the following table each row is a new villager, assuming a civilization that starts with 3 villagers.

\newpage

\renewcommand{\arraystretch}{1.2}

\begin{center}
\begin{tabular}{p{0.05\textwidth}|p{0.2\textwidth}|p{0.6\textwidth}}
 \# & Job & Notes \\
 \hline
 4 & sheep & Remember to keep the sheep directly below the TC. \\
 5 & sheep & \\
 6 & sheep & \\
 7 & wood & Build a lumber camp adjacent to the wood line. \\
 8 & wood & \\
 9 & wood & \\
 10 & wood & \\
 11 & boar & Have this vil build a house on the way to the boar. \\
 12 & berries & Build a mill one tile away from the bushes. \\
 13 & berries & \\
 14 & berries & \\
 15 & berries & \\
 16 & boar & This makes 8 vils on animals. Distribute them between boar and sheep.\\
 17 & farms & Farms on the right of the TC are slightly more efficient. \\
 18 & farms & \\
 19 & farms & \\
 20 & wood & Try to find a second wood line, so defending is easier.\\
 21 & wood & \\
 22 & wood & \\
 23 & wood & \\
 24 & farms & Also transfer a vil from animals to farms.\\
 25 & gold & Build a mining camp right next to the gold mine and transfer a vil from animals to gold.\\
 26 & gold & \\
 & \emph{Click Feudal} & While going up, keep scouting and if berries or animals run out, move those vils to farms and wood.\\
 27 & gold & Meanwhile build a blacksmith and another feudal building (depending on your game plan).\\
 28 & gold & \\
 & \emph{Click Castle} & Move any idle vils to wood and farms.
\end{tabular}
\end{center}

%\begin{thebibliography}{1}
%
%\bibitem{resonance22fc} 
%Resonance22
%\textit{Aoe2 Tutorial: Fast Castle Age, Knight Rush Build, Economy Boom}. 
%\url{https://www.youtube.com/watch?v=zQ5NOGLd3PE}
%
%\end{thebibliography}

\end{document}
